Exploring the Shadows of Terror: The Influence of Terrorism on Public Opinion and Democratic Values

### 2024-02-15 outputs/paper/paper.qmd
Final Commit

```{r }
#| label: fig-terrorism-trend
#| fig-cap: Summary of Data Included in the Meta-Analysis
#| echo: false
#| warning: false
#| message: false
#| out.width: "90%"  # Adjust to fit the page
#| out.height: "90%"  # Adjust to fit the page

@@

We used the following additional packages: broom [@broom], dotwhisker [@dotwhisker], cowplot [@cowplot], metafor [@metafor] in R [@citeR] to create @fig-reactions-to-terrorism.

@@

Investigating terrorism’s effects through public attitudes towards politics is necessary to detect the social reaction to such thought-provoking disasters. Starting from Amélie Godefroidt’s pioneering study (@Godefroidt2023), this paper takes her insights further and tries to bring in more deterministic factors that may work towards shaping public opinion related to terrorism. However, both Mia and I agree on the implications of ethics, limitations, and future hopeful prospects.
## Findings

@@

Our study builds upon and extends the insightful work of Amélie Godefroidt (@Godefroidt2023), presenting new perspectives on the influence of terrorism on political attitudes. Through comprehensive analysis and extension of previous research, it highlights the significant ways in which terrorism leads shifts towards outgroup hostility, political conservatism, and affects public opinion across various contexts. This paper underscores the importance of considering the sociopolitical environment when evaluating the impact of terrorism and suggests a nuanced understanding of its effects is important for formulating policies. In moving forward, we suggest an inclusive approach to research that encompasses a broader spectrum of terrorist ideologies and embraces different methodologies to capture the influence of terrorism in our society. This approach not only contributes to the academic discussion on terrorism and democracy but also offers practical insights for policymakers to navigate the challenges posed by terrorism.

>>>>

\newpage
```{r }
#| label: fig-terrorism-trend
#| fig-cap: Summary of Data Included in the Meta-Analysis
#| echo: false
#| warning: false
#| message: false
#| out.width: "90%"  # Adjust to fit the page
#| out.height: "90%"  # Adjust to fit the page

@@

We used the following additional packages: `broom` [@broom], `dotwhisker` [@dotwhisker], `cowplot` [@cowplot], `metafor` [@metafor] in `R` [@citeR] to create @fig-reactions-to-terrorism.

@@

Investigating terrorism’s effects through public attitudes towards politics is necessary to detect the social reaction to such thought-provoking disasters. Starting from Amélie Godefroidt’s pioneering study [@Godefroidt2023], this paper takes her insights further and tries to bring in more deterministic factors that may work towards shaping public opinion related to terrorism. However, we all agree on the implications of ethics, limitations, and future hopeful prospects.

## Findings

@@

Our study builds upon and extends the insightful work of Amélie Godefroidt [@Godefroidt2023], presenting new perspectives on the influence of terrorism on political attitudes. Through comprehensive analysis and extension of previous research, it highlights the significant ways in which terrorism leads shifts towards outgroup hostility, political conservatism, and affects public opinion across various contexts. This paper underscores the importance of considering the sociopolitical environment when evaluating the impact of terrorism and suggests a nuanced understanding of its effects is important for formulating policies. In moving forward, we suggest an inclusive approach to research that encompasses a broader spectrum of terrorist ideologies and embraces different methodologies to capture the influence of terrorism in our society. This approach not only contributes to the academic discussion on terrorism and democracy but also offers practical insights for policymakers to navigate the challenges posed by terrorism.
